\subsection{Research}
\subsubsection{Problem}

Currently there is no framework available to easily prototype multi-agent \acs{uav} systems in a simple environment. Creating a flexible multi-agent architecture would provide an effective solution for developers that want to start prototyping \acs{uav} systems. In this project 
the architectures of a multi-agent system must be demonstrated with examples. A generic solution must be found for creating easy prototyping.
Examples of how to use the different architectures must be present with documentation on how to create them.

In case a company/person wants to develop such technologies, they have to start off from scratch which would mean they 
to invest time/money into developing such environments. Using this project, it would erase the issue of a developer having 
to create their own environment. With examples of the architectures allready built-in it has the ability to boost a project by months.

The current state of the project is a proof of concept with a single \acs{uav}, developed for firefighters to give live feedback from the air, scanning the area for possible dangerous chemicals.

\subsubsection{Question}

How can a flexible \acs{mas} architecture for robotics be used in rapid \acs{uav} prototyping

\subsubsection{Sub-questions}
\begin{enumerate}
    \item What is an Agent?
    \item What is a \acs{mas}?
    \item What is a \acs{mas} architecture?
    \item What is a blackboard communication system?
    \item What are the advantages of a \acs{mas}
    \item What are the necessary/core components of a \acs{mas} architecture?
    \item Are there usable off-the-shelf rapid robot/\acs{uav} prototyping \acs{mas} architectures?
    \item What are the pros and cons of off-the-shelve rapid robot/\acs{uav} prototyping \acs{mas} architectures?
  \end{enumerate}
\newpage

\subsubsubsection{What is an Agent?}
\input{sections/chapters/Research/WhatIsAnAgent.tex}
\newpage

\subsubsubsection{What is a \acs{mas}?}
\input{sections/chapters/Research/WhatIsMAS.tex}
\newpage

\subsubsubsection{What is a \acs{mas} architecture?}
\input{sections/chapters/Research/WhatIsAMASArch.tex}
\newpage

\subsubsubsection{What is a blackboard communication system?}
\input{sections/chapters/Research/BlacKBoardCommunication.tex}
\newpage

\subsubsubsection{What are the advantages of a \acs{mas}}
\input{sections/chapters/Research/AdvantageOfMAS.tex}

\subsubsubsection{What are the necessary/core components of a \acs{mas} architecture?}
\input{sections/chapters/Research/ComponentsMAS.tex}
\newpage

\subsubsubsection{Are there usable off-the-shelf rapid robot/UAV prototyping \acs{mas} architectures?}
\input{sections/chapters/Research/premadeMASArch.tex}
\newpage

\subsubsubsection{What are the pros and cons of off-the-shelve rapid robot/UAV prototyping \acs{mas} architectures?}
\input{sections/chapters/Research/ProsAndConsPremade.tex}
\newpage

\subsubsection{Research method}
\input{sections/chapters/Research/ResearchMethod.tex}
\newpage